---
title: "Mapping"
author: "Nat Koonmee"
date: '2022-10-22'
output: html_document
---


```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(include = FALSE)

library("readxl")
library(dplyr)
library(ggpubr)
library(tidyverse)
library(ggplot2)
library(gapminder)
library(TSstudio)
library(hrbrthemes)
library(scales)
library(lubridate)
library(caret)
library(plotly)
library(openintro)
```

### Data Source

we got US population by race from https://worldpopulationreview.com/states/states-by-race \newline
and we got the resident population from www.census.gov \newline
\newline

Those both datasets are open source that anyone can legally download it.



### Loading data
```{r, include = T}

df <- read.csv("Mapping.csv")
# df$State <- df$State %>%
#   abbr2state() %>%
#   tolower()

df$Resident.Population <- as.numeric(gsub(",", "", df$Resident.Population))

for (i in  6:56){
  df[i, 1] = sub('^.(.*)', '\\1' , df[i, 1])
}
df <- df[6:56, ]

df$State <- df$State %>% tolower()

# a = "39,512,223"
# as.numeric(gsub(",", "", a))
```

```{r, include = F}
map1 <- map_data("state") %>% 
  mutate(region = str_to_lower(region)) %>% 
  left_join(df, by = c("region" = "State"))
map1
```


### US population
```{r, include = TRUE}
us_pop <- ggplot(data = map1,
                 mapping = aes(x = long, y = lat,
                               group = group,
                               fill = Resident.Population)) +
  geom_polygon(color = "white", size = .1) +
  theme_bw() +
  coord_map() +
  scale_fill_continuous(type = "viridis")+
  ggtitle("US resident population") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.title = element_blank())


us_pop

```

### Asian population in US
```{r, include = TRUE}
us_pop <- ggplot(data = map1,
                 mapping = aes(x = long, y = lat,
                               group = group,
                               fill = Asian)) +
  geom_polygon(color = "white", size = .1) +
  theme_bw() +
  coord_map() +
  scale_fill_continuous()+
  ggtitle("US resident population") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.title = element_blank())


us_pop

```

Those plot show the population in United State. We couls see that there are so many Asian race in CA, which make others state end up having the save colors



```{r, include=TRUE}
us_pop <- ggplot(data = map1,
                 mapping = aes(x = long, y = lat,
                               group = group,
                               fill = AsianTotalPerc)) +
  geom_polygon(color = "white", size = .1) +
  theme_bw() +
  coord_map() +
  scale_fill_continuous(type = "viridis")+
  ggtitle("US resident population") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.title = element_blank())

us_pop
```



After re-scale to see only the percentage, we can see that it is much easier to define Asian population in each State

















